---
name: Hanne 
surname: Oberman
position: "Statistician interested in metascience, open science, and interdisciplinarity"
address: ... # Padualaan 14, 3584 CH Utrecht
# phone: 
www: hanneoberman.github.io
email: "h.i.oberman@uu.nl"
twitter: hioberman
github: hanneoberman
linkedin: hanneoberman
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
profilepic: "avatar.jpg"
headcolor: 414141 #FFCD00
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me

 * I am very passionate about 'dull' or 'difficult' topics like statistics, programming, and philosophy of science.
 * I want to bring insights from different disciplines and methodologies together to solve complex real-world problems.
 * I am motivated to improve the quality of academic research *and* education. 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Graduated cum laude. Elective courses in Philosophy of Science.", "2018-2020", "MSc Methodology and Statistics for the Behavioural, Biomedical and Social Sciences", "Utrecht University",
  "Global Academy of Liberal Arts interdisciplinary conference and summer school.", "2018", "Graduate Summer School", "Concordia University, Montreal",
  "Interdisciplinary honours program Descartes College.", "2016-2018", "Honours Degree", "Utrecht University",
  "Graduated cum laude. Major in Cognitive Neurobiological Psychology. Minor in Governance for Sustainable Development, and Methods and Statistics in
the Social and Behavioral Science.", "2014-2018", "BSc Liberal Arts and Sciences", "Utrecht University"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Experience

```{r}
# tribble(
#   ~Year, ~Type, ~Desc,
#   1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#   1911, "Chemistry", "Awarded for the discovery of radium and polonium"
# ) %>% 
#   brief_entries(
#     glue::glue("Nobel Prize in {Type}"),
#     Year, 
#     Desc
#   )
tribble(
  ~Year, ~Job, ~Desc, ~Where,
  "since 2020", "Junior researcher", "Data visualization for uncertainty/missing data. With Dr. Gerko Vink and Prof. Dr. Stef van Buuren.", "Utrecht University",
  "since 2019", "Research assistant", "Developing novel methods to improve the validity of social scientific prediction. With Dr. Dong Nguyen and Dr. Daniel Oberski.", "Utrecht University",
  "since 2017", "Teaching assistant", "Teaching Methodology and Statistics and Experimental Psychology courses at all undergraduate levels. Task varying from practical supervision to lecturing, and from leading workgroups to grading assignments.", "Utrecht University",
  "2012-2017", "Hospitality and food sector jobs", "As a student, I have always worked part-time in restaurants and at a sustainable food start-up. Tasks include supervision of a team of 5-10 collegues, customer service, and account management.", "E.g., Dudok Rotterdam",
) %>%
  detailed_entries(
    Desc,
    Year,
    Job, 
    Where
  )
```

# Extracurricular
```{r}
tribble(
  ~Year, ~Job, ~Desc, ~Where,
  "since 2020", "Think tank", "Providing feedback and advice to the management teams of the Faculty of Social and Behavioural Sciences.", "Utrecht University",
  "since 2019", "Board", "Founder and treasurer of the Methodology And Statistics Alumni Society (MASAS). Tasks include planning events and developing the network.", "MASAS",
  "2019-2020", "Educational committee", "General member of the student council Faculty of Social and Behavioural Sciences  Research Masters.", "Utrecht University",
    "2018-2020", "Programme advisory committee", "Student representative Methodology and Statistics for the Behavioural, Biomedical and Social Sciences.", "Utrecht University",
  "2017-2018", "Educational committee", "President of the student council Liberal Arts and Sciences; vicepresident of the educational committee.", "Utrecht University",
  "2014-2018", "Board and committees", "I have been an active member of the study association Liberal Arts and Sciences, USLAS Atlas. Positions include vice-president of the association, president of the parents' day committee, secretary of the travel committee, and student-mentorship.", "USLAS Atlas",
) %>%
  detailed_entries(
    Desc,
    Year,
    Job, 
    Where
  )
```

# Grant and awards
```{r}
tribble(
  ~Year, ~Job, ~Desc, ~Where,
  "2019", "Best poster", "Social and Behavioural Sciences Graduate Poster Fair. Poster presentation about scientific practices around non-significant results: 'Will You Publish Null Papers?', in collaboration with Jerry Wenzel.", "Utrecht University",
  "2018", "Fellowship award", "Global Academy of Liberal Arts Annual Conference 'Creativity and the Liberal Arts' (HUMA 887).", "Concordia University, Montreal",
) %>%
  detailed_entries(
    Desc,
    Year,
    Job, 
    Where
  )
```

# Conferences
```{r}
tribble(
  ~Year, ~Job, ~Desc, ~Where,
  "", "Pre-study poster presentation", "Society for the Improvement of Psychological Science (SIPS) conference. Title: 'ShinyMICE: Developing a Missing Data Evaluation Suite (Master's Thesis Methodology and Statistics)'", "SIPS 2019",
  "", "Showcase", "Global Academy of Liberal Arts (GALA) Annual Conference. Title 'Creativity and the Liberal Arts'.", "GALA 2018",
  "", "Invited talk", "European Liberal Education Student Conference (LESC). Title: 'Creating Creativity? Assessing adaptive expertise in Liberal Education students'.", "LESC 2017",
  "", "Poster presentation", "Utrecht Platform for Creativity in Education (UPCE) conference. Title: 'Assessing Adaptive Expertise in Higher Education Students'", "UPCE 2016",
  "", "Workshop", "National Interdisciplinary Education (NIE) Conference. Title: 'The interdisciplinary research process in practice'.", "NIE 2016",
  
) %>%
  detailed_entries(
    Desc,
    Year,
    Job, 
    Where
  )
```

# Publications

```{r}
# library(dplyr)
# scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
#   filter(cites > 30) %>% 
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>% 
#   RefManageR::as.BibEntry() %>% 
#   RefManageR::WriteBib("curie.bib")
# 
#bibliography_entries("curie.bib")
```

